---
title: "R Notebook"
output: html_notebook
---

# Basic Idea

This project tries to analyze the car brands mentioned in lyrics.

# Import Packages

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
```


# Import Data

```{r}
load(file="../data/lyrics.RData")
lrc <- dt_lyrics
```

# Data Cleaning

```{r}
# keep songs' year from 1968-2016
lrc <- lrc%>%filter(year>=1968 & year <=2016)
# remove duplicated rows
lrc <- unique(lrc)
# remove songs with no lyrics or too many lyrics
lrc <- lrc%>%mutate(word_ct=str_count(lrc$lyrics, '\\w+'))
wd_outliers = boxplot(lrc$word_ct, plot=FALSE)$out
'%ni%' <- Negate('%in%')
lrc <- lrc%>%filter(lrc$word_ct %ni% wd_outliers)
```

# Data Analysis

Let's have a look at how many songs in each genre after data cleaning.
```{r}
lrc_genre <- lrc%>%group_by(genre)%>%summarise(genre_ct=n())%>%arrange(desc(genre_ct))
lrc_genre
```

It turns out "Rock" has the most songs in this dataset.

How many cars are mentioned in lyrics?
```{r}
# lexus
lexus <- sum(grepl("\\lexus\\b", lrc$lyrics, ignore.case = TRUE))
lexus

# ferari
ferari <- sum(grepl("rari", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("ferari", lrc$lyrics, ignore.case = TRUE))
ferari

# bentley
bentley <- sum(grepl("bentley", lrc$lyrics, ignore.case = TRUE))
bentley

# bmw
bmw <- sum(grepl("bmw", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("beamer", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("bimmer", lrc$lyrics, ignore.case = TRUE)) 
bmw

# lamborghini
lambo <- sum(grepl("lambo", lrc$lyrics, ignore.case = TRUE))
lambo

# maserati
maserati <- sum(grepl("maserati", lrc$lyrics, ignore.case = TRUE))
maserati

# mcLaren
mclaren <- sum(grepl("mclaren", lrc$lyrics, ignore.case = TRUE))
mclaren

# benz
benz <- sum(grepl("\\benz\\b", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("\\mercedes\\b", lrc$lyrics, ignore.case = TRUE)) +  sum(grepl("\\benzi\\b", lrc$lyrics, ignore.case = TRUE))
benz

# porsche
porsche <- sum(grepl("porsche", lrc$lyrics, ignore.case = TRUE))
porsche

# amg
amg <- sum(grepl("\\amg\\b", lrc$lyrics, ignore.case = TRUE))
amg

# cadillac
caddy <- sum(grepl("cadillac", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("caddy", lrc$lyrics, ignore.case = TRUE))
caddy

# ford
ford <- sum(grepl("\\ford\\b", lrc$lyrics, ignore.case = TRUE))
ford

# honda
honda <- sum(grepl("honda", lrc$lyrics, ignore.case = TRUE))
honda

#toyota
toyota <- sum(grepl("toyota", lrc$lyrics, ignore.case = TRUE))
toyota

# nissan
nissan <- sum(grepl("nissan", lrc$lyrics, ignore.case = TRUE))
nissan

# volvo
volvo <- sum(grepl("volvo", lrc$lyrics, ignore.case = TRUE))
volvo

# chevrolet
chevy <- sum(grepl("chevrolet", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("chevy", lrc$lyrics, ignore.case = TRUE))

# jeep
jeep <- sum(grepl("jeep", lrc$lyrics, ignore.case = TRUE))
jeep

# buick
buick <- sum(grepl("buick", lrc$lyrics, ignore.case = TRUE))
buick

# jaguar
jaguar <- sum(grepl("jaguar", lrc$lyrics, ignore.case = TRUE))
jaguar

# land rover
rover <- sum(grepl("\\rover\\b", lrc$lyrics, ignore.case = TRUE))
rover

# lexus
audi <- sum(grepl("\\audi\\b", lrc$lyrics, ignore.case = TRUE)) + sum(grepl("\\audis\\b", lrc$lyrics, ignore.case = TRUE))
audi

# tesla
tesla <- sum(grepl("tesla", lrc$lyrics, ignore.case = TRUE))
tesla

cars <- tibble('lexus'=lexus, 'ferari'=ferari, 'bentley'=bentley, 'bmw'=bmw, 'lambo'=lambo, 'maserati'=maserati, 'mclaren'=mclaren, 'benz'=benz, 'porsche'=porsche, 'amg'=amg, 'caddy'=caddy, 'ford'=ford, 'honda'=honda, 'toyota'=toyota, 'nissan'=nissan, 'volvo'=volvo, 'chevy'=chevy, 'jeep'=jeep, 'buick'=buick, 'jaguar'=jaguar, 'rover'=rover, 'audi'=audi, 'tesla'=tesla)
cars <- cars%>%pivot_longer(everything(), names_to = "car brand", values_to = "count")%>%arrange(desc(count))
cars <- cars%>%mutate(percentage=count/sum(count)*100)
cars
```

It turns out "Cadillac" is the most mentioned car brand among all songs.

So my next question is: What genre mentions cars most?
It can be seen from the above tibble that top 4 car brands count for nearly 70% among all brands. 
So I work on these four brands:
```{r}
# cadilac
lrc_caddy <- lrc%>%mutate(caddy=(grepl("cadillac", lrc$lyrics, ignore.case = TRUE)) | grepl("caddy", lrc$lyrics, ignore.case = TRUE))%>%filter(caddy==TRUE)
lrc_caddy <- lrc_caddy%>%group_by(genre)%>%summarise(caddy_count=n())%>%arrange(desc(caddy_count))
lrc_car <- lrc_genre%>%left_join(lrc_caddy)%>%mutate(caddy_percentage=caddy_count/genre_ct*100)

# chevrolet
lrc_chevy <- lrc%>%mutate(chevy=(grepl("chevrolet", lrc$lyrics, ignore.case = TRUE)) | grepl("chevy", lrc$lyrics, ignore.case = TRUE))%>%filter(chevy==TRUE)
lrc_chevy <- lrc_chevy%>%group_by(genre)%>%summarise(chevy_count=n())%>%arrange(desc(chevy_count))
lrc_car <- lrc_car%>%left_join(lrc_chevy)%>%mutate(chevy_percentage=chevy_count/genre_ct*100)

# ferari
lrc_ferari <- lrc%>%mutate(ferari=(grepl("rari", lrc$lyrics, ignore.case = TRUE)) | grepl("ferari", lrc$lyrics, ignore.case = TRUE))%>%filter(ferari==TRUE)
lrc_ferari <- lrc_ferari%>%group_by(genre)%>%summarise(ferari_count=n())%>%arrange(desc(ferari_count))
lrc_car <- lrc_car%>%left_join(lrc_ferari)%>%mutate(ferari_percentage=ferari_count/genre_ct*100)

# jeep
lrc_jeep <- lrc%>%mutate(jeep=grepl("jeep", lrc$lyrics, ignore.case = TRUE))%>%filter(jeep==TRUE)
lrc_jeep <- lrc_jeep%>%group_by(genre)%>%summarise(jeep_count=n())%>%arrange(desc(jeep_count))
lrc_car <- lrc_car%>%left_join(lrc_jeep)%>%mutate(jeep_percentage=jeep_count/genre_ct*100)

# Add up all the percentage w/i genre
lrc_car <- lrc_car%>%select(genre, caddy_percentage, chevy_percentage, ferari_percentage, jeep_percentage)
lrc_car <- lrc_car%>%mutate(sum=caddy_percentage+chevy_percentage+ferari_percentage+jeep_percentage)%>%arrange(desc(sum))
lrc_car
```

# Conclusion
It seems like "Other" genre has the most cars mentioned. But have a look at the singers: "a-boogie-wit-da-hoodie", "asap twelvyy", "g-herbo"... are rappers so their songs should belong to "Hip-Hop". Thus the conclusion would be "Hip-Hop" songs mention cars most in our dataset. And among all car brands, "Cadillac" is singers' favourite choice.


